P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2024-01-09 manuscript.tex
Add highlights
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

>>>>

%%Research highlights
\begin{highlights}
\item A DSL and code generator for performance-portable particle simulations is introduced
\item Different algorithms such as Linked Cells and Verlet Lists can be generated
\item Generated codes can solve Molecular Dynamics and Discrete Element Method simulations
\item Base and scaling performances are shown for CPUs and GPUs in both Fritz and JUWELS-Booster clusters
\item Optimization aspects and strategies of Molecular Dynamics and Discrete Element Method simulations are discussed
\end{highlights}
